\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-16 icse/compiler.tex
Written 4.4 Rule Assistant

\subsection{Rule Generation Assistant}

\inred{
To make easy write compile rules, we support \textit{rule generation assistant}.
It consists of two helper functions; the \textit{rule recommender} and
the \textit{fault localizer}. The

It makes easy not only construct compile rules from the scratch
but also updates existing compile rules to handle specification updates.
We explain each helper function and how to utilize it to construct compile rules.

\subsubsection{Statistics Monitor}

TODO

\subsubsection{Fault localizer}

TODO
}

>>>>

\subsection{Rule Assistant}

To make easy write compile rules, we support \textit{rule assistant}.
It takes currently not yet convertible steps as arguments
and we call them as failed steps. For each failed step,
The rule assistant diagnosis the root cause of parsing failures.
The basic idea is to check that it becomes possible to be parsed
with assumption that a speicific sub-sequence of failed steps is
successfully parsed. We define the approach to find such sub-sequences of
failed steps as \textit{fault localizations}. The rule assistant recommend
new compile rules for failed steps via fault localizations.
Moreover, it also helps us update existing compile rules for new version
of specifications.

The fault localization algorithm is evaluated with the special token \( \tstar \).
The special token \( \tstar \) represents a sub-sequence of a failed step.
The rule assistant substitues a specific sub-sequence \( T[i..j] \) of the
failed step \( T \) into a single star token \( \tstar \). For each compile rule,
the parsing rule  \( \code{starT} \) is implicitely added to utilize it in the
rule assistant. The \( \code{starT} \) is a special basic token parser
that just checks whether the given token is the special token \( \tstar \).
Its corresponding conversion rule is a function that returns a dummy
\( \ires \) component \( \code{Dummy} \) with the String value of the
compile rule name. For example, the compile rules in the previous example are
acutally defined as follows:
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = ... | starT ^^ { case x => Dummy("Stmt") }
// expressions
val Expr = ... | starT ^^ { case x => Dummy("Expr") }
\end{lstlisting}
Then, the rule assistant evaluates the \textsc{FaultLocalize} algorithm
with the failed step to find the set of most specific suggestions.
\begin{algorithm}
  \caption{Fault Localization}
  \begin{algorithmic}[1]
    \Function{FaultLocalize}{$T,n$}\Comment{$T$ - failed step, $n$ - size}
    \State $S = \varnothing$
    \For{$i = 0$ to $n - 1$}
    \For{$j = i$ to $n - 1$}
    \State $T'$ = a copy of $T$
    \State Substitue $T'[i..j]$ into $\tstar$
    \If{Parse($T'$) containing $\code{Dummy(}x \code{)}$}
    \State Insert $(x, i, j)$ into $S$
    \EndIf
    \EndFor
    \EndFor
    \While{$s = (x, i, j) \in S$}
    \If{$\exists (y, p, q) \in S$ s.t. $i \leq p \wedge q \leq j$}
    \State Remove $s \in S$
    \EndIf
    \EndWhile
    \State \Return $S$
    \EndFunction
  \end{algorithmic}
\end{algorithm}

For example, assume that the expression compile rule for lists is removed.
Then, the step 2-e-i of the ToPrimitive algorithm becomes a failed step.
The fault localization algorithm first find one suggestion for statements
and four suggestions for expressions as follows:
\[
  \begin{array}{c}
    (\code{"Stmt"}, 0, 14), \;
    (\code{"Expr"}, 3, 13), \;
    (\code{"Expr"}, 4, 13), \;\\
    (\code{"Expr"}, 6, 12), \;
    (\code{"Expr"}, 10, 12)
  \end{array}
\]
However, first four suggestions are removed because the last one is the most
specific sub-sequence. Finally, the rule assistant suggests to define
another expression compile rule for the token list \hint{}.
